Turbulence in compact to giant HII regions

### 2022-02-11 strucfunc_paper.tex
Javier changes 2022-02-11

A more common pattern for structure functions of HII regions looks like a 'hook' where at large separations the structure function values start decreasing.
This behavior is shown in the Orion core, 30 Doradus, Hubble V, NGC 595 and the EON.
Less common is the behavior where at large separations there are also a series of ascending values in the structure function, like the Lagoon nebula or NGC 346, or a periodic behavior like NGC 604.
The precise reasons of this change on the structure function at large-scales is out of the scope of this investigation.

@@

Ideally the correlation length \(r_0\) should represent the scale of dominant energy injection.
It is unclear what are the mechanisms driving the turbulence, thought a lot of options are candidates.
The main energy sources are, of the order of kpc, the differential rotations of the galaxy that produces shear at large scale, at scales of the order of hundreds of pc, supernova explosions inject a large amount of kinetic energy.
At scales of several tens of pc the expansion of \hii{} regions is also a source of energy and bipolar flows, shocks, and jets inject energy at small scales, about one tenth of a pc.
\cite{2011MNRAS.413..705L} also discuss the possibility of turbulent motions initiated by champagne flows and stellar winds. 
The velocity fluctuations are consequence of the combination of the various mechanism already mentioned and wouldn't be correct to attribute these fluctuations solely to one mechanism.
The complexity of the extraction of pure turbulent motions from velocity profiles in nebulae is not just an observational problem, there is also the lack of precise information on how these mechanism contribute to the emission line broadening \citep{2011MNRAS.413..705L,arthur2016turbulence}.

@@

The index \(m\) is shown in the last column of Table \ref{tab:Res} and is commonly used as a reference for comparison between observations and the theoretic value of 0.67 (equation \ref{eq:velocity-moments}).
All indices are above this theoretic value and the interpretation of this difference is that the analyzed regions do not comply with the properties established in the development of the turbulence theory.

From section~\ref{sec:regions-milky-way} we know that most of all assumption mentioned in section~\ref{sec:turbulence-theory} are not meet for our \hii{} region sample.
\hii{} regions emerged from a molecular cloud with highly filamentary and clumpy density structure .
There is a large increase in the temperature because of the photoionization and the density gradients with the pressure gradients accelerate the flow which occurs in multiple scale consequences of the fractal nature of the molecular cloud \citep{arthur2016turbulence}.
This would result in a inhomogeneous structure characteristic of \hii{ } regions as it is possible to observe in Figure~\ref{fig:hii-regions}.
The incompressible and subsonic conditions in the flow are clearly not meet since there is evidence of the presence of shock fronts and supersonic velocity values.
This a a consequences of the inhomogeneous structure mentioned in the paragraph above and other processes as O star winds and radiation pressure which would also aid in the stirring of the gas.
And as \hii{} regions are regarded as three-dimensional objects there is also the possibility of a sheet-like distribution which could overcome this assumption.

For all these reason is expected that \hii{} regions power-law indices do not follow the classic 0.67 value.
But despite the complex nature of \hii{} regions we observe a common pattern for the structure function and the value of the index falls in a certain limited range of values

%\subsubsection{Projection smearing}\label{sec:projection-smearing}
%As a justification for the use of the structure function we can consider that any relation between the line width and line-of-sight depth can be interpreted in terms of a correlation between velocity spread and scale size.
%This follows that if we have an optically thin spectral line where it will have a width which is related to the total radial velocity dispersion of all fluctuations sampled along the line-of-sight \citep{1984ApJ...277..556S}. 
%In these sense the structure function is used as a tool to investigate the projection of a three-dimensional correlation function onto the plane of sky \citep{arthur2016turbulence}.

%It have been mentioned that the projection of the velocity fluctuations reduces the actual amplitude in the line-of-sight \citep{1984ApJ...277..556S,arthur2016turbulence}.
%We can see from Table \ref{tab:Res} that the line-of-sight velocity dispersion is roughly twice the plane-of-sky velocity dispersion.
%In the case of homogeneous turbulent velocity we can consider the effect of \textit{project smearing} \citep{1984ApJ...277..556S}, where the projection from three to two dimensions over the line-of-sight depth \(H\), reduces the plane-of-sky amplitude for the condition \(r_{0} < H\).
%With a value of \(\sigma\pos / \sigma_{\text{los}}\) = 0.5 we obtain \(r_{0} / H \sim\) 0.02-0.1.

@@

\begin{equation}\label{eq:projection-smearing-3d}
m_{2D}= m_{3D} + 1
\end{equation}

or when the astronomical object is almost two-dimensional (sheet-like) we have:

\begin{equation}\label{eq:projection-smearing-2d}
m_{2D} \sim m_{3D}
\end{equation}

If the extension of the HII region is compared with its depth (three-dimensional case) the value of the index is 1.6. 
While the case where the extension is much greater than its depth (two-dimensional case) the region will have a value of 0.6 \citep{von1951methode, munch1958internal,1987ApJ...317..686O}.

We can compute the \(m_{3D}\) index from the two dimensional \(m\), if we assume that the \(m_{3D}\) index lies between the limits of projection smoothing and a sheet-like distribution. 
Following the procedure by \cite{arthur2016turbulence} and assuming the relationship \(m_{2D} - 1 < m_{3D}\ < m_{2D}\) we have 0.54 \(< m_{3D} <\) 0.72.

@@

%sigma pos vs sigma los
The standard deviation of the velocity centroid and the mean non-thermal linewidth allow us to compare the relation between the kinematical disorder on the plane-of-the sky and along the line-of-sight  \citep{2011MNRAS.413..705L}.

The broad in the velocity width of the emission line represents the range of velocities along the line-of-sight.%, among thermal movements. 
We can consider as a main broadening mechanisms the kinematical disorder along the LOS related to velocity gradients by the clumpiness on the molecular cloud and turbulent movements.
On the plane-of-sky the consequences of those gradients and movements is measured in every pixel. 
The spatial variations on the velocity field would depend on the targeted pixel, depending on the motions inside the cloud (the LOS component).
This reasoning has lead to \citet{2011MNRAS.413..705L} to propose a direct relationship between \(\sigma_{\text{LOS}}\) and \(\sigma\pos\).

%The Figure \ref{fig:svss} shows the log \(\sigma\)-log \(\sigma_{\text{los}}\) plane with a relationship of \(\log \sigma\pos = (0.76 \pm 0.48) \log \sigma_{\text{los}}-(0.14 \pm 0.54)\).

>>>>

A more common pattern for structure functions of HII regions looks like a 'hook' where at large separations the structure function values start decreasing.
This behavior is shown in the Orion core, 30 Doradus, Hubble V, NGC 595 and the EON.
Less common is the behavior where at large separations there are also a series of ascending values in the structure function, like the Lagoon nebula or NGC 346, or a periodic behavior like NGC 604.

@@

Ideally the correlation length \(r_0\) should represent the scale of dominant energy injection.
It is unclear what are the mechanisms driving the turbulence, thought a lot of options are candidates.
The main energy sources are, of the order of kpc, the differential rotations of the galaxy that produces shear at large scale, at scales of the order of hundreds of pc, supernova explosions inject a large amount of kinetic energy.
At scales of several tens of pc the expansion of \hii{} regions and stellar winds are also a source of energy and bipolar flows, shocks,jets and champagne flows inject energy at small scales, about one tenth of a pc.
The velocity fluctuations are consequence of the combination of the various mechanism already mentioned and wouldn't be correct to attribute these fluctuations solely to one mechanism.
The complexity of the extraction of pure turbulent motions from velocity profiles in nebulae is not just an observational problem, there is also the lack of precise information on how these mechanism contribute to the emission line broadening \citep{2011MNRAS.413..705L,arthur2016turbulence}.

@@

The index \(m\) shown in the last column of Table \ref{tab:Res} is used for comparison between observations and the theoretical value of 0.67 (equation \ref{eq:velocity-moments}).
All our indices are above this theoretical value and this is attributed to the fact that the analyzed regions do not comply with the assumptions established in the development of the turbulent theory.

From section~\ref{sec:regions-milky-way} we know that most of all assumption mentioned in section~\ref{sec:turbulence-theory} are not meet for our \hii{} region sample.
\hii{} regions emerged from a molecular cloud with highly filamentary and clumpy density structure .
There is a large increase in the temperature because of the photoionization and the density gradients with the pressure gradients accelerate the flow which occurs in multiple scale, consequence of the fractal nature of the molecular cloud \citep{arthur2016turbulence}.
The radiation pressure, stellar winds and region expansion, among other physical processes would create pressure-driven shock waves propagating faster than the speed of sound in the medium.
This would regard conditions in \hii{} regions as compressible and supersonic.
And as \hii{} regions are regarded as three-dimensional objects there is the possibility of a sheet-like distribution which could overcome this assumption.
%This would result in a inhomogeneous density structure where arcs, filaments and shells are characteristic of \hii{ } regions as we can see from Figure~\ref{fig:hii-regions}.

But despite the complex nature of \hii{} regions we observe a common pattern for the structure function and the value of the index we obtain falls in a certain limited range of values. 
The differences with respect the theoretical value are often used as a diagnostic tools to identify properties that are not consider in the assumptions of the turbulence theory.

@@

\begin{equation}\label{eq:projection-smearing-3d}
m_{2D}= m_{3D} + 1
\end{equation}
%
or when the astronomical object is almost two-dimensional (sheet-like):
%
\begin{equation}\label{eq:projection-smearing-2d}
m_{2D} \sim m_{3D}
\end{equation}

As a conclusion, if the extension of the HII region is compared with its depth (three-dimensional case) the value of the index is 1.6. 
While the case where the extension is much greater than its depth (two-dimensional case) the region will have a value of 0.6 \citep{von1951methode, munch1958internal,1987ApJ...317..686O}.

%We can compute the \(m_{3D}\) index from the two dimensional \(m\), if we assume that the \(m_{3D}\) index lies between the limits of projection smoothing and a sheet-like distribution. 
%Following the procedure by \cite{arthur2016turbulence} and assuming the relationship \(m_{2D} - 1 < m_{3D}\ < m_{2D}\) we have 0.54 \(< m_{3D} <\) 0.72.

@@

%The broad in the velocity width of the emission line represents the range of velocities along the line-of-sight.%, among thermal movements. 
%We can consider as a main broadening mechanisms the kinematical disorder along the LOS related to %velocity gradients by the clumpiness on the molecular cloud and turbulent movements.
%On the plane-of-sky the consequences of those gradients and movements is measured in every pixel. 
%The spatial variations on the velocity field would depend on the targeted pixel, depending on the motions inside the cloud (the LOS component).
%This reasoning has lead to \citet{2011MNRAS.413..705L} to propose a direct relationship between \(\sigma_{\text{LOS}}\) and \(\sigma\pos\).

As a justification for the use of the structure function we can consider that any relation between the line width and line-of-sight depth can be interpreted in terms of a correlation between velocity spread and scale size.
This follows that if we have an optically thin spectral line where it will have a width which is related to the total radial velocity dispersion of all fluctuations sampled along the line-of-sight \citep{1984ApJ...277..556S}. 
In these sense the structure function is used as a tool to investigate the projection of a three-dimensional correlation function onto the plane of sky \citep{arthur2016turbulence}.

The standard deviation of the velocity centroid, \(\sigma\pos\), and the mean non-thermal linewidth, \(\sigma_{\text{LOS}}\), allow us to compare the relation between the kinematical disorder on the plane-of-the sky and along the line-of-sight  \citep{2011MNRAS.413..705L}.
It have been mentioned that the projection of the velocity fluctuations reduces the actual amplitude in the line-of-sight \citep{1984ApJ...277..556S,arthur2016turbulence}.

We can see from Table \ref{tab:Res} that the line-of-sight velocity dispersion is roughly twice the plane-of-sky velocity dispersion.

%In the case of homogeneous turbulent velocity we can consider the effect of \textit{project smearing} \citep{1984ApJ...277..556S}, where the projection from three to two dimensions over the line-of-sight depth \(H\), reduces the plane-of-sky amplitude for the condition \(r_{0} < H\).
%With a value of \(\sigma\pos / \sigma_{\text{los}}\) = 0.5 we obtain \(r_{0} / H \sim\) 0.02-0.1.
